Automated Essay Scoring

### 2018-05-10 paper/acl17-latex/paper.tex
Added abstract

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of ACL-2017. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL
and NAACL proceedings, including those for ACL 2017 by Dan Gildea and
Min-Yen Kan, NAACL-2017 by Margaret Mitchell, ACL-2012 by Maggie Li
and Michael White, those from ACL-2010 by Jing-Shing Chang and Philipp
Koehn, those for ACL-2008 by Johanna D. Moore, Simone Teufel, James
Allan, and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal
Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and
earlier ACL and EACL formats. Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Recent advances in deep learning have produced state of art results in
  the task of automated essay scoring. The performance of these
  systems are not tested are approaching human level in the evaluation metrics,
  but their performance in actual scenarios is not explored. In this paper we explore
  how well these systems perform in real life scenarios as compared to non-neural
  models. We also explore some ways to overcome these shortcomings.
\end{abstract}

@@

There is a recent surge in use of deep learning for the task of automated essay scoring.
These models have shown to out perform the traditional models based on hand coded features
and currently have the state of art performance in this task. The current state of art model
is from Taghipour et al. \cite{nea}
